Reassessing the Impact of Dynamic Slicing in SFL

### 2019-02-08 paper/ijcai/paper.tex
remove appendix

\begin{appendices}
	\section{Other data that might be interesting to report}
	This section has the only purpose of presenting and discussing other data that 
	are not intended yet to be used in the paper. If you find something interesting 
	in this block of information, please report.

	\begin{table}[h]
		\centering
		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ccc}
			\toprule
			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
			\midrule
			$<0$  & 19.2\% & 15.4\% \\ 
			$=0$  & 23.1\% & 26.9\% \\ 
			$>0$  & 57.7\% & 57.7\% \\

			\bottomrule
		\end{tabular}
		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagchart}
	\end{table}
	\normalsize

	\begin{table}[h]
		\centering
		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ccc}
			\toprule
			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
			\midrule
			$<0$  & 40.7\% & 33.3\% \\ 
			$=0$  & 25.9\% & 18.5\% \\ 
			$>0$  & 33.3\% & 48.1\% \\

			\bottomrule
		\end{tabular}
		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagtime}
	\end{table}
	\normalsize

	\begin{table}[h]
		\centering
		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ccc}
			\toprule
			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
			\midrule
			$<0$  & 36.8\% & 28.9\% \\ 
			$=0$  & 26.3\% & 28.6\% \\ 
			$>0$  & 36.8\% & 50.0\% \\

			\bottomrule
		\end{tabular}
		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagmockito}
	\end{table}
	\normalsize

	\begin{table*}[h]
		\setlength{\tabcolsep}{3pt}
		\begin{tabular}{llllllllllllll}
			\toprule
			   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
		top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
		top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
			   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
		top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
		top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
			\bottomrule
		\end{tabular}
		\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
		\label{table:reduction}
	\end{table*}

	\begin{table*}[h]
		\small
		\setlength{\tabcolsep}{3pt}
		\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
		\toprule
			   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
		SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
		\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
		$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
		\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
		$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
		& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
		SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
		\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
		$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
		\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
		$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
		\bottomrule
		\end{tabular}
		\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 ($\Delta-5$) and top-10 ($\Delta-10$) of the faulty classes}
		\label{table:performance}
	\end{table*}
	\normalsize

\end{appendices}

>>>>

% \begin{appendices}
% 	\section{Other data that might be interesting to report}
% 	This section has the only purpose of presenting and discussing other data that
% 	are not intended yet to be used in the paper. If you find something interesting
% 	in this block of information, please report.
%
% 	\begin{table}[h]
% 		\centering
% 		\setlength{\tabcolsep}{4pt}
% 		\begin{tabular}{ccc}
% 			\toprule
% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
% 			\midrule
% 			$<0$  & 19.2\% & 15.4\% \\
% 			$=0$  & 23.1\% & 26.9\% \\
% 			$>0$  & 57.7\% & 57.7\% \\
%
% 			\bottomrule
% 		\end{tabular}
% 		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
% 		\label{tab:diagchart}
% 	\end{table}
% 	\normalsize
%
% 	\begin{table}[h]
% 		\centering
% 		\setlength{\tabcolsep}{4pt}
% 		\begin{tabular}{ccc}
% 			\toprule
% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
% 			\midrule
% 			$<0$  & 40.7\% & 33.3\% \\
% 			$=0$  & 25.9\% & 18.5\% \\
% 			$>0$  & 33.3\% & 48.1\% \\
%
% 			\bottomrule
% 		\end{tabular}
% 		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
% 		\label{tab:diagtime}
% 	\end{table}
% 	\normalsize
%
%
% 	\begin{table}[h]
% 		\centering
% 		\setlength{\tabcolsep}{4pt}
% 		\begin{tabular}{ccc}
% 			\toprule
% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
% 			\midrule
% 			$<0$  & 36.8\% & 28.9\% \\
% 			$=0$  & 26.3\% & 28.6\% \\
% 			$>0$  & 36.8\% & 50.0\% \\
%
% 			\bottomrule
% 		\end{tabular}
% 		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
% 		\label{tab:diagmockito}
% 	\end{table}
% 	\normalsize
%
% 	\begin{table*}[h]
% 		\setlength{\tabcolsep}{3pt}
% 		\begin{tabular}{llllllllllllll}
% 			\toprule
% 			   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
% 		top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
% 		top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
% 			   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
% 		top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
% 		top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
% 			\bottomrule
% 		\end{tabular}
% 		\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
% 		\label{table:reduction}
% 	\end{table*}
%
% 	\begin{table*}[h]
% 		\small
% 		\setlength{\tabcolsep}{3pt}
% 		\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
% 		\toprule
% 			   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
% 		SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
% 		\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
% 		$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
% 		\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
% 		$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
% 		& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
% 		SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
% 		\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
% 		$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
% 		\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
% 		$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
% 		\bottomrule
% 		\end{tabular}
% 		\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 ($\Delta-5$) and top-10 ($\Delta-10$) of the faulty classes}
% 		\label{table:performance}
% 	\end{table*}
% 	\normalsize

% \end{appendices}
